Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model

### 2020-06-22 paper/paper.tex
20200622 10:57:00

@@

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual ground-state entropy. The spin-1/2 Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model. Khaliullin \emph{et al.,} \cite{Khaliullin2005, PhysRevLett.102.017205} proposed to realized this highly anisotropic spin model in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates $A_2$IrO$_3$ (A = Na, Li). In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra. The resulting Hamiltonian is the Heisenberg-Kitaev (HK) model. It was later extended to contains more terms such as the off-diagonal $\Gamma$ term \cite{PhysRevLett.112.077204}. In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a))and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}. Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=1/2 models with edge sharing octahedra \cite {PhysRevLett.112.077204}. Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the HK model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained. However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.

@@

Inspired by previous theoretical and experimental works, we study the Heisenberg-Kitaev-$\Gamma$ ($J-K-\Gamma$) model on the triangular lattice. The $J-K-\Gamma$ model Hamiltonian is given by
\begin{equation}
    H=\sum_{\langle i,j \rangle \in \alpha \beta (\gamma)} \lbrack J \bm{S}_i \bm{\cdot} \bm{S}_j + K S_i^{\gamma} S_j^{\gamma} + \Gamma (S_i^{\alpha} S_j^{\beta} + S_i^{\beta} S_j^{\alpha}) \rbrack \label{eq:Hamiltonian}
\end{equation}
where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.~\ref{fig:ModelDefinition}(b), and $\alpha$, $\beta$ are the remaining directions. $J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions and $\Gamma$ the symmetric off-diagonal exchanges. To the best of our knowledge, no exact solution has been reported so far for the spin-1/2 Kitaev and/or $\Gamma$ model on the triangular lattice. Therefore, it remains conceptually interesting to investigate whether the QSL could exist as a possible ground state of the triangular $J-K-\Gamma$ model.

\begin{figure}
    \includegraphics[width=\columnwidth]{Fig1.pdf}
    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame. (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation, see tha main text for detailed information.}
\end{figure}

@@

To have further insight into these phases, we adopt the method introduced in Ref~\onlinecite{PhysRevB.94.064435} to extract the moment directions for some of these phases. For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction. The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction). In other words, the ordered moment of the FM-B phase is in the direction of the $x,y,z$-axis. As for stripe ordered states, there are three degenerate patterns in real space as shown in Fig.~\ref{fig:PhaseDiagram}(b)-(d) and the ordered moment is locked to the orientation of the stripe pattern. Since the cluster spin-coherent state is captured only by a single pair of $(\theta, \phi)$ for collinear states (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$. For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps for the representative model parameters of the Stripe-A and Stripe-D phase are shown in Fig.~\ref{fig:Proabilities}(a) and Fig.~\ref{fig:Proabilities}(b). The probability map for the Stripe-A phase has high intensity at $(\pi/2, 0)$ and $(\pi/2, \pi)$ which means the ordered moment would along the $x$-axis direction. The Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for stripe pattern in Fig.~\ref{fig:PhaseDiagram}(b) from classical considerations, our ED results show that this situation also applies at quantum limit. On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(b) indicates that the ordered moment pointing to the $y$ and $z$-axis direction. The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(b), $\pm x$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(c), $\pm x$, $\pm y$ for Fig.~\ref{fig:PhaseDiagram}(d)), more importantly it is a signature of large quantum flucations in the GS. It is worth to note that even the GS of the classical AF Kitaev model was identified to be highly degenerate involving nematic and stripe ordered states, our ED results favor the idea that quantum flucations would select stripe ordered states as GS out of an otherwise infinitely degenerate manifold of classical states. This selection of states among a continuum is the so called \emph{order-from-disorder} mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.

@@

For these areas marked as Stripe-B and Stripe-C in the global phase diagram, the representative SMSF profiles are shown in Fig.~\ref{fig:StructureFactors}(d) and Fig.~\ref{fig:StructureFactors}(e). For all of these model parameters, the SMSF peaked at the M-points indicating stripe ordered GS in these areas. To test the presence of the classical stripe ordered states, we construct cluster spin-coherent states based on the spin pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(e) and Fig.~\ref{fig:Proabilities}(f). When $\alpha=0.7\pi,\beta=0.66\pi$, the probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, whereas $P(\theta, \phi)$ is clearly peaked at the direction given by Eq.~\eqref{eq:v0} for $\alpha=0.3\pi, \beta=0.25\pi$. Considering the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the exact cluster GS, it is reasonable to say that the stripe ordered ground states for the classical $J-K-\Gamma$ model in these areas persist in the quantum limit and the ordered moments of the quantum states coincide with their classical analogue. The reduced probabilities $P_{max} < \frac{1}{6}$ may be attributed to quantum flucations. In the HK limit, there exist a stripe phase (i.e., Stripe-A) when $J>0, K<0$ and the ordered moment along the $x,y,z$-axis direction. When an infinitesimal $\Gamma$ interaction is included, both positive and negative couplings tilting the ordered moment orientation away from the cubic axes directions, yielding the Stripe-B phase. The ordered moment orientation of the Stripe-B phase is given by Eq.~\eqref{eq:v1} and its equivalents (see Appendix~\ref{apx:AppendixB} for details).
%When $\Gamma \rightarrow 0^{+}$ or $\Gamma \rightarrow 0^{-}$, the direction determined by Eq.~\eqref{eq:v1} tend to be the same as the $x$-axis direction which means the phase transition from positive $\Gamma$ to negative $\Gamma$ is continuous.%
As for the Stripe-D phase near the AF Kitaev point, the effect of the $\Gamma$ term is again tilting the ordered moment away from the cubic axes directions though the effects for positive and negative couplings are different. An infinitesimal positive $\Gamma$ interaction changes the ordered moment orientation from the cubic axes directions to the direction specified by Eq.~\eqref{eq:v0} and its equivalents (see Appendix~\ref{apx:AppendixB} for details). On the other hand, when an infinitesimal negative $\Gamma$ interaction is introduced, the ordered moment is rotated to the direction determined by Eq.~\eqref{eq:v1} and its equivalents.

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig5.pdf}
    \caption{\label{fig:Spectrum}(Color online) (a) The k-points in the first Brillouin zone corresponding to a 4 $\times$ 6 cluster with 4 lattice sites along the $x$-bond direction and 6 lattice sites along the $y$-bond direction. (b) Spin excitation spectrum for $\alpha=0.05\pi,\beta=0.10\pi$. The $A(\bm{k}, \omega)$ is draw along the path shown in (a).}
\end{figure}

@@

\section{\label{sec:SectionV}Summary}
In summary, by using classical Monte Carlo simulation and exact diagnoalization we map out the global phase diagram of both the classical and quantum $J-K-\Gamma$ model. The global phase diagram of the quantum model is analogus to its classical counterpart except a small area of QSL near the antiferromagetic $\Gamma$ point. We propose the QSL to be gapped based on the spin excitation spectrum. Apart from this QSL phase, we also provide detailed description of the distinctions between those collinear phases. Especially, we propose the GS of the antiferromagetic Kitaev model to be a stripe ordered state and the ordered moment along the $x, y, z$-axis direction.

@@

\subsection{$J=\Gamma=0, K=1$}
The ground state for the classical antiferromagetic Kitaev model is also degenerate involving three nematic ordered states and three stripe ordered states. For the nematic ordered state shown in Fig.~\ref{fig:GSForPositiveK}(a), the spins on the chains along the $x$-bond direction form antiferromagetic chains and the direction for the orange arrow is $[100]$. There is no association between different chains. Similarly, the antiferromagetic chains along the $y$-bond and $z$-bond direction for Fig.~\ref{fig:GSForPositiveK}(b) and Fig.~\ref{fig:GSForPositiveK}(c) respectively. The direction for the orange arrow in Fig.~\ref{fig:GSForPositiveK}(b) is $[010]$ and in Fig.~\ref{fig:GSForPositiveK}(c) is $[001]$. In addition to these nematic ordered states, there are stripe ordered states that have the same energy as the nematic ordered states. For the stripe ordered states shown in Fig.~\ref{fig:GSForPositiveK}(d)-(f), the corresponding ordered moment lie in the $yz$, $xz$ and $xy$ plane, respectively.
\begin{figure}
    \includegraphics[width=0.5\textwidth]{FigA3.pdf}
    \caption{\label{fig:GSForPositiveK}(Color online) Nematic and stripe ground state spin configurations for $J=\Gamma=0, K=1$.}
\end{figure}

>>>>

\author{Wei Wang}
\affiliation{School of Science, Nanjing University of Posts and Telecommunications (NUPT), Nanjing 210023, China}

@@

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual ground-state entropy. The spin-1/2 Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model. Khaliullin \emph{et al.,} \cite{Khaliullin2005, PhysRevLett.102.017205} proposed to realized this highly anisotropic spin model in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates $A_2$IrO$_3$ (A = Na, Li). In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra. The resulting Hamiltonian is the Heisenberg-Kitaev (HK) model. It was later extended to contains more terms such as the off-diagonal $\Gamma$ term \cite{PhysRevLett.112.077204}. In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)) and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}. Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=1/2 models with edge sharing octahedra \cite {PhysRevLett.112.077204}. Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the HK model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained. However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.

@@

Inspired by previous theoretical and experimental works, we study the Heisenberg-Kitaev-$\Gamma$ ($J-K-\Gamma$) model on the triangular lattice. The $J-K-\Gamma$ model Hamiltonian is given by
\begin{equation}
    H=\sum_{\langle i,j \rangle \in \alpha \beta (\gamma)} \lbrack J \bm{S}_i \bm{\cdot} \bm{S}_j + K S_i^{\gamma} S_j^{\gamma} + \Gamma (S_i^{\alpha} S_j^{\beta} + S_i^{\beta} S_j^{\alpha}) \rbrack \label{eq:Hamiltonian}
\end{equation}
where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.~\ref{fig:ModelDefinition}(c), and $\alpha$, $\beta$ are the remaining directions. $J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions and $\Gamma$ the symmetric off-diagonal exchanges. To the best of our knowledge, no exact solution has been reported so far for the spin-1/2 Kitaev and/or $\Gamma$ model on the triangular lattice. Therefore, it remains conceptually interesting to investigate whether the QSL could exist as a possible ground state of the triangular $J-K-\Gamma$ model.

\begin{figure}
    \includegraphics[width=\columnwidth]{Fig1.pdf}
    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame. (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation, see the main text for detailed information.}
\end{figure}

@@

To have further insight into these phases, we adopt the method introduced in Ref~\onlinecite{PhysRevB.94.064435} to extract the moment directions for some of these phases. For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction. The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction). In other words, the ordered moment of the FM-B phase is in the direction of the $x,y,z$-axis. As for stripe ordered states, there are three degenerate patterns in real space as shown in Fig.~\ref{fig:PhaseDiagram}(b)-(d) and the ordered moment is locked to the orientation of the stripe pattern. Since the cluster spin-coherent state is captured only by a single pair of $(\theta, \phi)$ for collinear states (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$. For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps for the representative model parameters of the Stripe-A and Stripe-D phase are shown in Fig.~\ref{fig:Proabilities}(a) and Fig.~\ref{fig:Proabilities}(b). The probability map for the Stripe-A phase has high intensity at $(\pi/2, 0)$ and $(\pi/2, \pi)$ which means the ordered moment would along the $x$-axis direction. The Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for stripe pattern in Fig.~\ref{fig:PhaseDiagram}(b) from classical considerations, our ED results show that this situation also applies at quantum limit. On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(b) indicates that the ordered moment pointing to the $y$ and $z$-axis direction. The small $P_{max}$ of about 2\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(b), $\pm x$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(c), $\pm x$, $\pm y$ for Fig.~\ref{fig:PhaseDiagram}(d)), more importantly it is a signature of large quantum flucations in the GS. It is worth to note that even the GS of the classical AF Kitaev model was identified to be highly degenerate involving nematic and stripe ordered states, our ED results favor the idea that quantum flucations would select stripe ordered states as GS out of an otherwise infinitely degenerate manifold of classical states. This selection of states among a continuum is the so called \emph{order-from-disorder} mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.

@@

For these areas marked as Stripe-B and Stripe-C in the global phase diagram, the representative SMSF profiles are shown in Fig.~\ref{fig:StructureFactors}(d) and Fig.~\ref{fig:StructureFactors}(e). For all of these model parameters, the SMSF peaked at the M-points indicating stripe ordered GS in these areas. To test the presence of the classical stripe ordered states, we construct cluster spin-coherent states based on the spin pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(e) and Fig.~\ref{fig:Proabilities}(f). When $\alpha=0.7\pi,\beta=0.66\pi$, the probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, whereas $P(\theta, \phi)$ is clearly peaked at the direction given by Eq.~\eqref{eq:v0} for $\alpha=0.3\pi, \beta=0.25\pi$. Considering the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the exact cluster GS, it is reasonable to say that the stripe ordered ground states for the classical $J-K-\Gamma$ model in these areas persist in the quantum limit and the ordered moments of the quantum states coincide with their classical analogue. The reduced probabilities $P_{max} < \frac{1}{6}$ may be attributed to quantum flucations. In the HK limit, there exist a stripe phase (i.e., Stripe-A) when $J>0, K<0$ and the ordered moment along the $x,y,z$-axis direction. When an infinitesimal $\Gamma$ interaction is included, both positive and negative couplings tilting the ordered moment orientation away from the cubic axes directions, yielding the Stripe-B phase. The ordered moment orientation of the Stripe-B phase is given by Eq.~\eqref{eq:v1} and its equivalents (see Appendix~\ref{apx:AppendixB} for details).

As for the Stripe-D phase near the AF Kitaev point, the effect of the $\Gamma$ term is again tilting the ordered moment away from the cubic axes directions though the effects for positive and negative couplings are different. An infinitesimal positive $\Gamma$ interaction changes the ordered moment orientation from the cubic axes directions to the direction specified by Eq.~\eqref{eq:v0} and its equivalents (see Appendix~\ref{apx:AppendixB} for details). On the other hand, when an infinitesimal negative $\Gamma$ interaction is introduced, the ordered moment is rotated to the direction determined by Eq.~\eqref{eq:v1} and its equivalents.

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig5.pdf}
    \caption{\label{fig:Spectrum}(Color online) Spin excitation spectrum for $\alpha=0.05\pi,\beta=0.10\pi$. $A(\bm{k}, \omega)$ is draw along the path $M-\Gamma-M-\Gamma$.}
\end{figure}

@@

\section{\label{sec:SectionV}Classical Monte Carlo Phase Diagram}
We begin with paralleling-tempering Monte Carlo \cite{JPSJ.65.1604} on 40 replicas with temperature $T/J$ ranging from 0.001 to 1.0. For each replica, we sample it with a combination of heat-bath \cite{Miyatake_1986} and over-relaxation method \cite{Berg2004MarkovCM} mainly on a $24 \times 24$ triangle lattice with periodic boundary contitions. A whole MC step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice. We perform $10^6$ MC steps per replica, then, we copy out the spin configuration from the lowest-T replcia, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the ground state. The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
\begin{equation}
    \mathbf{S}_i = \frac{\mathbf{h}_i^{loc}}{|\mathbf{h}_i^{loc}|}S
\end{equation}
with
\begin{equation}
    \mathbf{h}_i^{loc} = \sum_{<j>} JS_j + KS_j^{\gamma}\hat{e}^{\gamma} + \Gamma (S_j^{\alpha}\hat{e}^{\beta} + S_j^{\beta}\hat{e}^{\alpha})
\end{equation}
For some competing states, we start from several different initial configurations in order to obtain the correct classical ground state.

From the magnetic configuration of ground state, we compute the spin structure factor given by:
\begin{equation}
    \mathbf{S}_k = \frac{1}{N} \sum_{ij} \langle \mathbf{S}_i \cdot \mathbf{S}_j \rangle e^{i \mathbf{k} \cdot (\mathbf{r}_i - \mathbf{r}_j)}
\end{equation}
which is one of the key character to identify magnetic phases.

\begin{figure*}
    \centering
    \includegraphics[width=0.96\textwidth]{Fig6.pdf}
    \caption{\label{fig:ClassicalPhaseDiagram}(Color online) Classical global phase diagram of the triangular lattice $J-K-\Gamma$ model from Monte Carlo simuations.}
\end{figure*}

\section{\label{sec:SectionVI}Summary}
In summary, by using classical Monte Carlo simulation and exact diagnoalization we map out the global phase diagram of both the classical and quantum $J-K-\Gamma$ model. The global phase diagram of the quantum model is analogus to its classical counterpart except a small area of QSL near the antiferromagetic $\Gamma$ point. We propose the QSL to be gapped based on the spin excitation spectrum. Apart from this QSL phase, we also provide detailed description of the distinctions between those collinear phases. Especially, we propose the GS of the antiferromagetic Kitaev model to be a stripe ordered state and the ordered moment along the $x, y, z$-axis direction.

@@

\subsection{$J=\Gamma=0, K=1$}
The ground state for the classical antiferromagetic Kitaev model is also degenerate involving three nematic ordered states and three stripe ordered states. For the stripe ordered states shown in Fig.~\ref{fig:GSForPositiveK}(a)-(c), the corresponding ordered moment lie in the $yz$, $xz$ and $xy$ plane, respectively. In addition to these stripe ordered states, there are nematic ordered states that have the same energy as the stripe ordered states. For the nematic ordered state shown in Fig.~\ref{fig:GSForPositiveK}(d), the spins on the chains along the $x$-bond direction form antiferromagetic chains and the direction for the pink arrows are $[100]$. There are no association between different chains. Similarly, the antiferromagetic chains along the $y$-bond and $z$-bond direction for Fig.~\ref{fig:GSForPositiveK}(e) and Fig.~\ref{fig:GSForPositiveK}(f) respectively. The direction for the lightgreen arrows in Fig.~\ref{fig:GSForPositiveK}(e) and lightyellow arrows in Fig.~\ref{fig:GSForPositiveK}(f) are $[010]$ and $[001]$, respectively.
\begin{figure}
    \includegraphics[width=0.5\textwidth]{FigA3.pdf}
    \caption{\label{fig:GSForPositiveK}(Color online) Nematic and stripe ground state spin configurations for $J=\Gamma=0, K=1$.}
\end{figure}
